Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Abstract
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@24 db7c848b-7755-4df2-b763-8796797afa52

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
  We present the features, algorithms and system integration necessary to
  implement a parallel rendering framework usable in a wide range of real-world
  research and industry applications, based on the basic architecture and
  implementation of the Equalizer parallel rendering framework presented in
  \cite{EMP:09}.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Parallel Rendering, Scalable Visualization, Cluster Graphics, Immersive Environments, Display Walls
\end{IEEEkeywords}}

@@

Tile (\fig{fig:tile}) and chunk decompositions are a variant of sort-first and
sort-last rendering, respectively. They decompose the scene into a predefined
set of fixed-size image tiles or database ranges. These tasks are queued and
processed by all source channels by polling a server-central queue. Prefetching
ensures that the task communication overlaps with rendering. As shown in
\cite{SPEP:16}, these modes provide better performance due to being inherently
load-balanced, as long as there is an insignificant overhead for the render task
setup. This mode is transparent to Equalizer applications.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
  \begin{abstract}
    Developing complex, real world applications which utilize multiple GPUs and
    computers for 3D interactive rendering tasks can be a daunting task, in
    particular since it requires expertise in distributed systems and parallel
    rendering in addition to the application domain. We present a mature
    parallel rendering framework which provides a large set of features,
    algorithms and system integration for a wide range of real-world research
    and industry applications. Based on the basic architecture and
    implementation of the Equalizer parallel rendering framework presented in
    \cite{EMP:09}, we show how the generic algorithms are integrated in the
    framework to help application development in many different domains.
  \end{abstract}

  % Note that keywords are not normally used for peerreview papers.
  \begin{IEEEkeywords}
    Parallel Rendering, Scalable Visualization, Cluster Graphics, Immersive Environments, Display Walls
  \end{IEEEkeywords}
}

@@

Tile (\fig{fig:tiles}) and chunk decompositions are a variant of sort-first and
sort-last rendering, respectively. They decompose the scene into a predefined
set of fixed-size image tiles or database ranges. These tasks are queued and
processed by all source channels by polling a server-central queue. Prefetching
ensures that the task communication overlaps with rendering. As shown in
\cite{SPEP:16}, these modes provide better performance due to being inherently
load-balanced, as long as there is an insignificant overhead for the render task
setup. This mode is transparent to Equalizer applications.
